---
title: "W241 Final Project: Subliminal Investigation"
date: "12/10/2020"
author: "Amit Karandikar"
output: pdf_document
---

```{r load packages, warning=FALSE, echo=FALSE, message=FALSE}
library(data.table)
library(sandwich)
library(lmtest)
library(AER) 
library(ggplot2) 
library(patchwork)
```

```{r load and clean survey response data}
d <- fread('./data/survey-responses.csv', header = TRUE)

# Questions 8 - 17 are the quiz
setnames(
  x = d,
  old =c("SC0","Q_RecaptchaScore","Q2","Q3","Q4","Q6",
         "Q18","Q19","Q20","Q21","Q26"),
  new =c("score","bot_response","interest","experience",
         "sub_treatment","sub_control","used_ext",
         "gender","age","education",
         "country")
)
# make all columns lowercase
setnames(d, tolower(names(d[1:ncol(d)])))

# Remove invalid data if experience has NA values - no randomization occurred
d <-d[!is.na(experience)]

# count the no of questions answered
d[,questions_attempted:=(10 - (is.na(q8) + is.na(q9) + + is.na(q10) +
                      is.na(q11)+ is.na(q12)+ is.na(q13) + 
                      is.na(q14)+ is.na(q15)+ is.na(q16)+ is.na(q17)))]

# convert posix timestamps into dates
d[,`:=`(startdate=as.POSIXct(startdate), enddate=as.POSIXct(enddate))]

# Remove pilot group as well as those uninterested in Data Science (Question 2)
d <- d[startdate > '2021-11-12 19:00' & interest == 1 ]

# Remove Bot responses (scores will be less than 0.5)
# d <- d[bot_response >= 0.5]
paste('Total valid responses: ',nrow(d))


# mark treatment and control groups
d[,subliminal:=ifelse(test = d[,is.na(sub_treatment)], 0, 1)]
d[,experience_ind:=ifelse(test = d[,experience > 2], 1, 0)]
paste('No of people in treatment', nrow(d[subliminal==1]))
paste('No of people in control', nrow(d[subliminal==0]))
```
```{r}
hist(d[which(d$subliminal == 0) ,]$score,  
     xlim = c(0,10),
     ylim = c(0, 100), col = "red", 
     border = F, 
     main = "Frequency of scores in treatment and control groups", 
     xlab = "Scores", density=20, angle = 120)

hist(d[which(d$subliminal == 1),]$score, 
     xlim = c(0,10),
     ylim = c(0, 100), col= "blue", 
     add=T, density = 20)

```
```{r}
require(ggplot2)

dplot <- rbind(data.frame(group="Control", questions_answered = d[which(d$subliminal == 0) ,]$questions_attempted),
               data.frame(group="Treatment", questions_answered = d[which(d$subliminal == 1) ,]$questions_attempted))

ggplot(dplot, aes(x=questions_answered, fill=group, )) +
  geom_histogram(binwidth=1, colour="black", position="dodge") +
  theme(legend.position = "right") + scale_fill_manual(name="Priming", values =  c("#F8766D", "#00BFC4"))
```

# Calcuate the average treatment effect

```{r ate}
ate_model <- d[,lm(score ~ subliminal)]
summary(ate_model, vcov=vcovHC)
```

# Effect of blocking

```{r blocking}
# indicator variable instead of factor , novice 0, expert 1
ate_blocking <- d[,lm(score ~ subliminal + experience_ind)]
summary(ate_blocking)
```
For this model, the estimated difference in treatment means is the average of the within-block differences. Individuals within each block are intended to be more similar based on their experience in working in the field of Data Science, and as a result, the variability of the within-block differences is expected to be smaller than the variability between two units randomly chosen from all units in the population.


# All Covariates Model
```{r all covariates included}
ate_all_cov_model <- d[,lm(score ~ subliminal + gender
                           + age + education + country 
                           + experience_ind
                           + subliminal*education + subliminal*gender)]
summary(ate_all_cov_model)
```

```{r}
stargazer::stargazer(ate_model, ate_blocking, type = 'text', 
                     column.labels = c('Model 1','Model 2'), 
                     dep.var.labels = c('Quiz Score'),
                     covariate.labels = c('subliminal priming','experience'))
```

```{r}
stargazer::stargazer(ate_model, ate_blocking, ate_all_cov_model, type = 'text')
```


```{r}
require(dplyr)
dplot <- rbind(data.frame(group="Treatment", question=1, correctly_answered = as.numeric(summary(d[which(d$subliminal == 1)]$q8 == 1)['TRUE'])),
               data.frame(group="Control", question=1, correctly_answered = as.numeric(summary(d[which(d$subliminal == 0)]$q8 == 1)['TRUE'])), 
               data.frame(group="Treatment", question=2, correctly_answered = as.numeric(summary(d[which(d$subliminal == 1)]$q9 == 3)['TRUE'])),
               data.frame(group="Control", question=2, correctly_answered = as.numeric(summary(d[which(d$subliminal == 0)]$q9 == 3)['TRUE'])), 
               data.frame(group="Treatment", question=3, correctly_answered = as.numeric(summary(d[which(d$subliminal == 1)]$q10 == 3)['TRUE'])),
               data.frame(group="Control", question=3, correctly_answered = as.numeric(summary(d[which(d$subliminal == 0)]$q10 == 3)['TRUE'])), 
               data.frame(group="Treatment", question=4, correctly_answered = as.numeric(summary(d[which(d$subliminal == 1)]$q11 == 2)['TRUE'])),
               data.frame(group="Control", question=4, correctly_answered = as.numeric(summary(d[which(d$subliminal == 0)]$q11 == 2)['TRUE'])), 
               data.frame(group="Treatment", question=5, correctly_answered = as.numeric(summary(d[which(d$subliminal == 1)]$q12 == 2)['TRUE'])),
               data.frame(group="Control", question=5, correctly_answered = as.numeric(summary(d[which(d$subliminal == 0)]$q12 == 2)['TRUE'])), 
               data.frame(group="Treatment", question=6, correctly_answered = as.numeric(summary(d[which(d$subliminal == 1)]$q13 == 1)['TRUE'])),
               data.frame(group="Control", question=6, correctly_answered = as.numeric(summary(d[which(d$subliminal == 0)]$q13 == 1)['TRUE'])), 
               data.frame(group="Treatment", question=7, correctly_answered = as.numeric(summary(d[which(d$subliminal == 1)]$q14 == 3)['TRUE'])),
               data.frame(group="Control", question=7, correctly_answered = as.numeric(summary(d[which(d$subliminal == 0)]$q14 == 3)['TRUE'])), 
               data.frame(group="Treatment", question=8, correctly_answered = as.numeric(summary(d[which(d$subliminal == 1)]$q15 == 2)['TRUE'])),
               data.frame(group="Control", question=8, correctly_answered = as.numeric(summary(d[which(d$subliminal == 0)]$q15 == 2)['TRUE'])), 
               data.frame(group="Treatment", question=9, correctly_answered = as.numeric(summary(d[which(d$subliminal == 1)]$q16 == 1)['TRUE'])),
               data.frame(group="Control", question=9, correctly_answered = as.numeric(summary(d[which(d$subliminal == 0)]$q16 == 1)['TRUE'])), 
               data.frame(group="Treatment", question=10, correctly_answered = as.numeric(summary(d[which(d$subliminal == 1)]$q17 == 1)['TRUE'])),
               data.frame(group="Control", question=10, correctly_answered = as.numeric(summary(d[which(d$subliminal == 0)]$q17 == 1)['TRUE'])))


ggplot(dplot, aes(x = question, y = correctly_answered, fill=group)) +
  geom_col(position = "dodge") + scale_fill_manual(name="Priming",
  values =  c("#F8766D", "#00BFC4"))
```
```{r}
d[, correctly_answered_1:= ifelse(q8 == 1, 1, 0)]
d
```

```{r}
nrow(d[subliminal == 1 & correctly_answered_1==1])
```

```{r}
ate_blocking_for_q1 <- d[,lm(correctly_answered_1 ~ subliminal + experience_ind)]
summary(ate_blocking_for_q1)
```